\subsubsection{Cost Category 22.03: Auxiliary Cooling Systems}

The Cost Category 22.03, originally designated for auxiliary cooling, was primarily considered for cryogenic cooling systems related to magnets. It has been recommended that all cooling services, including those initially covered under Account 22.03, be directly associated with the specific account requiring those services. In this instance, the auxiliary cooling services for the magnets are to be included under Cost Category 22.02.04, which deals with Cryogenics for Plasma Confinement. Auxiliary Cooling Systems therefore currently consists of:

\begin{itemize}
    \item Cost Category 22.03.04 Power Supply and Cooling System: 
    \begin{itemize}
        \item Cost Category 22.03.04.01 Refrigeration: Systems for maintaining low temperatures in critical areas.
        \item Cost Category 22.03.04.02 Piping: Network of pipes for the distribution of cooling fluids.
        \item Cost Category 22.03.04.03 Fluid Circulation Driving System: Mechanisms for propelling cooling fluids throughout the system.
        \item Cost Category 22.03.04.04 Tanks: Storage units for cooling fluids or refrigerants.
        \item Cost Category 22.03.04.05 Purification: Processes to ensure the purity and effectiveness of cooling fluids.
    \end{itemize}
    \item Cost Category 22.03.05 Other Cooling Systems: Additional cooling systems not categorized elsewhere.
\end{itemize}

Costs are expressed as 30\% of the power supply costs to give a total of \$ C220300 M.