\subsubsection{Cost Category 22.06: Other Heat Island Equipment}

This Cost Category encompasses various essential components and systems of a reactor plant that are not specifically categorized elsewhere. This category is crucial for the comprehensive coverage of all necessary equipment in reactor plant operations and maintenance, safety and compliance.  This category includes, but is not limited to:


\begin{itemize}
    \item Cost Category 22.06.01 Maintenance Equipment
    \item Cost Category 22.06.01.01 Blanket Maintenance Equipment. Tools and systems for maintaining the blanket.
    \item Cost Category 22.06.01.02 Components Rotated into Service. Spare components used to replace operational ones during maintenance.
    \item Cost Category 22.06.01.03 Other. Miscellaneous equipment required for general maintenance activities.
    \item Cost Category 22.06.02 Special Heating Systems
    \item Cost Category 22.06.02.01 Start-up Systems. Equipment used for heating processes during start-up phases.
    \item Cost Category 22.06.03 Coolant Receiving, Storage and Make-up Systems.
    \item Cost Category 22.06.03.01 Coolant Handling. Systems for receiving, storing, and preparing coolant.
    \item Cost Category 22.06.04 Gas Systems
    \item Cost Category 22.06.04.01 Gas Handling and Management. Systems for managing gases used in or produced in the Heat Island.
    \item Cost Category 22.06.05 Building Vacuum Systems.
    \item Cost Category 22.06.05.01 Vacuum Maintenance. Systems to maintain vacuum conditions within certain Heat Island areas, crucial for operational integrity and safety.
\end{itemize}

Due to the broad nature of this cost category, bottom-up calculations are difficult to perform, without precise details and engineering designs. For costing purposes, we allocate 10\% of the cost of the Heat Island component (cost category 22.1) costs to this category, and the total budget is C220600 M USD.