
\subsection{Cost Category 24: Electric Plant Equipment}

Consists of the switchgear, station service eqiupment, switchboards, protective equipment, electrical structures and wiring containers, power and control wiring and electrical lighting.  Accounts 21 through 23 all have interfaces with the power plant electrical service system and its associated equipment. This equipment is located both inside and outside the main reactor/BOP buildings.

\begin{itemize}

\item Cost Category 24.01.00 Switchgear: Includes switchgear for the generator and station service, generator transformer, auxiliary transformer, and connecting bus (typically to 10kV).

\item  Cost Category 24.02.00 Station Service Equipment: Includes substations, auxiliary power sources, load centers, motor control centers, and station service and startup equipment, transformers, and bus ducts (typically to 500V).

\item  Cost Category 24.03.00 Switchboards: Includes control panels, auxiliary power and signal boards, batteries, DC equipment, and non-uninterruptible power.

\item  Cost Category 24.04.00 Protective Systems Equipment: Includes grounding systems, lightning protection, cathodic protection, heat tracing, freeze protection equipment, radiation monitoring, environmental monitoring equipment, raceway, cable, and connections. Excludes communication systems and building services such as lighting, HVAC, and fire protection (which are included in their respective building accounts).

\item  Cost Category 24.05.00 Electrical Raceway Systems: Includes cable tray, exposed conduits, embedded conduits, underground conduit and duct systems, and the fittings, supports, covers, boxes, access holes, ducts, and accessories for the scheduled cable systems. Excludes raceways for protective systems (Account 24.4) and building services electrical systems (which are included in their respective building
accounts).

\item  Cost Category 24.06.00 Power and Control Cables and Wiring: Typically includes all scheduled cable systems and their associated fittings such as cable, straps, attachments, terminations, wire lugs, cable numbers, and wire numbers. Excludes lighting, communication, and other protection systems.

\end{itemize}

Cost basis is the NETL baseline Case B12A, Cost Category 11: Accessory Electric Plant Bare erected cost excluding engineering, construction management, and contingency \$37 million in source table for Coal Plant / 686 MW electric capacity in source table = \$54/kW applied to gross  thermal power, to give a total of \$ C240000 M.