\subsubsection{Cost Category 22.07: Instrumentation and Control }

For a NOAK plant, it is anticipated that the I\&C technologies will be much more advanced than current  capabilities. This system will include the power core instrumentation and control, radiation and  monitoring equipment, isolated indicating and recording equipment, data acquisition and  recording, communication equipment, benchboards, panels, racks, process computers, I\&C tubing and fittings, instrumentation, and software, consisting of the following cost items:

\begin{itemize}
\item Cost Category 22.07.01 Heat Island Instrumentation and Control Equipment. Instrumentation and control equipment to monitor and manage the plasma and all  its related functional equipment contained in the Heat Island (includes all equipment in Account 22).

\item Cost Category 22.07.02 Radiation Monitoring Equipment. Monitoring equipment to ensure safe levels of radiation are maintained  during routine plant operations, determining the tritium inventories in all plant components, and  analyze/report any fault or accidental release of radioactive materials. 

\item Cost Category 22.07.03 Steam Turbine Control Equipment	

\item Cost Category 22.07.04 Other Major Component Control Equipment	

\item Cost Category 22.07.05 Signal Processing Equipment	

\item Cost Category 22.07.06 Control Boards, Panels, \& Racks	
\item Cost Category 22.07.07 Distributed Control System Equipment	
\item Cost Category 22.07.08 Instrument Wiring and Tubing	
\item Cost Category 22.07.09 Other Instrumentation \& Controls Equipment	


\end{itemize}


We use the NETL Case B31A Category 12 Instrumentation and Control for a 727MW Net power plant with bare erected costs of \$14M representing 19\$/kW.  Instrumentation in the heat island remains a major cost driver for FOAK, but by NOAK should come pre-packaged as multiple instrument packages, totalling \$ 50M, giving 88\$/kW.   We calculate \$ C220700 M for this cost category.