\subsubsection*{Cost Category 22.01.04: Compression System}

MIF compression systems can be driven electromagnetically, pneumatically, or mechanically.  There are therefore many compression systems and subsystems that can be considered.  Here we take as an illustrative example, the LINUS liquid metal liner system (see earlier sections on the background).\\

The LINUS fusion energy concept, developed as part of the Linus program, is based on the magnetized target fusion (MIF) principle (see earlier sections for a full literature review). The basic idea is to use the kinetic energy of an imploding liner to compress a plasma to high density and fusion temperature. The fusion energy design involves the dynamic compression of a magnetically-confined plasma by an imploding, rotating, liquid-metal liner, which helps suppress instabilities and protect components in the radial build from neutron flux. The concept envisions the nondestructive, repetitive, and reversible implosion of a liquid-metal cylindrical annulus onto a simply-connected magnetized plasma.\\

The major components of the LINUS concept are therefore:

\begin{itemize}
  \item Cost Category 22.01.04.01 Liquid Metal Injection System. Central to the LINUS concept, this system involves injecting liquid metal to form a stable, hollow cylindrical liner of rotating liquid metal (primaryC) for plasma containment and compression. It must maintain the hollow liquid cylinder's integrity under extreme pressures and incident heat flux.

    \item Cost Category 22.01.04.02 Axial Annular Actuators. Designed to induce radial implosion of the liquid metal, these actuators play a critical role in compressing the plasma, thereby increasing its temperature and density, essential for producing the fusion reaction.

    \item Cost Category 22.01.04.03 Pneumatic System. This system operates the axial annular actuators using a compressed gas. It ensures precise control over the timing and magnitude of the forces applied to the liquid metal for optimal plasma conditions.

    \item Cost Category 22.01.04.04 Diagnostic and Control System. Responsible for monitoring and controlling the entire LINUS setup, this system collects real-time data and adjusts the other components to maintain desired fusion conditions and ensure operational safety.
\end{itemize}

The cost totals \$ C220104 M for the system.

