\subsubsection{Cost Category 22.01: Heat Island Components}

The fusion system comprises various critical components, each playing a unique role in ensuring the effective and safe operation of the fusion process. These components are:

\begin{itemize}
    \item Cost Category 22.01.01 First Wall and Blanket. The first wall and blanket are crucial for protecting the reactor's interior from intense fusion reactions and for capturing and converting fusion energy into heat.
    
    \item Cost Category 22.01.02 Shield. The shield serves to protect surrounding structures and personnel from radiation produced during fusion, playing a key role in ensuring safety and regulatory compliance.
    
    \item Cost Category 22.01.03 Compression Lasers. In laser-driven fusion systems, lasers are used to drive the fuel implosion to initiate the fusion reaction.  These lasers have a longer pulse than ignition lasers.  
    
    \item Cost Category 22.01.04 Ignition Lasers. These lasers emit energy in short, intense bursts, with peak power reaching petawatts, and are used in 'fast ignition' concepts.
    
    \item Cost Category 22.01.05 Primary Structure and Support. The primary structure and support systems provide the necessary mechanical integrity and stability to the fusion reactor.
    
    \item Cost Category 22.01.06 Vacuum System. The vacuum system maintains the necessary vacuum conditions within the reactor chamber, which is crucial for the containment and control of the plasma.
    
    \item Cost Category 22.01.07 Power Supplies. These are essential for providing the electrical power needed for various reactor systems, including heating, cooling, and plasma confinement.
    
    \item Cost Category 22.01.08 Target Factory. In inertial confinement fusion systems, the target factory produces large quantity of the fusion targets required for the fusion reactions.

    \item Cost Category 22.01.09 Direct energy convertor. In some cases, energy can be directly converted from the exhaust plasma to electricity with higher conversion efficiency.
    
    \item Cost Category 22.01.11 Assembly and Installation. This encompasses the human resources involved in the assembly and installation of the fusion heat island components.

    \item Cost Category 22.01.19 Scheduled replacement costs.  Capitalized costs of components that will not serve the lifetime of the plant and be replaced on a schedule - usually the first wall and blanket, but can be components in other systems listed here (such as in the laser systems).
 \end{itemize}


Each of these major costs are examined in detail in the following sections.