\section{International Collaboration}
\subsection{Introduction}
\textit{Here we will assess the potential for international collaboration on MIF research and development, considering factors such as knowledge sharing, cost sharing, and risk mitigation. We will explore existing collaborations and propose new partnerships that could help accelerate the deployment of MIF.}  


\subsection{Regulations: US}

A key element of international collaboration is the regulations associated with military equipment. In the US, the International Traffic in Arms Regulations (ITAR) govern the export and import of military equipment, as listed on the United States Munitions List (USML) \cite{ecfrFederalRegister}. Some of the technologies required for fusion power may have potential millitary applications, so for effective international collaboration to occur, the regulations need to be considered.

To comply with ITAR, covered entities must register with the DDTC and obtain a license for the export of goods and services listed on the USML, including technical data. Registered entities are also required to maintain a comprehensive record of exported or temporarily imported defense goods, the identity of the recipients (end user), and the end-use (a specific way the item will be used) of the item or goods.

A second, much broader, regulatory framework in the US is the Export Administration Regulations (EAR) \cite{docExportAdministration}. The EAR, governed by the Bureau of Industry and Security, cover a wider range of dual-use items, including technologies and materials pertinent to nuclear fusion. These regulations are essential for overseeing the export and reexport of commercial items that may have strategic importance. The EAR classify various technologies and materials under Export Control Classification Numbers (ECCNs) within the Commerce Control List (CCL), which can include essential components used in nuclear fusion. Compliance with EAR is crucial for entities engaged in fusion research and international collaboration, ensuring adherence to national security and foreign policy objectives. Particularly sensitive systems include those handling lithium isotopes, tritium, and high-power pumping and cryogenics. 

Here, we present the systems and subsystems under category 22 (Heat Island Plant Equipment) of the Magnetic Mirror MIF reactor design specified in this report, and categorize their USML and EAR status. Note that in many cases, the relevant fusion technology is not directly listed in the CML or EAR. In these indirect categorisations, the item and category is still included as an indication, even if it is not explicitly listed. For a complete evaluation, experienced legal advice should be taken.



\begin{table}[h!]
    \centering
    \resizebox{1\linewidth}{!}{%
    \begin{tabular}{p{4cm}p{3cm}p{3cm}p{3cm}p{3cm}}
        \hline
        Cost Category & USML Coverage & Subsystem under USML & CCL Coverage & Subsystem under CCL \\
        \hline  
        20. Land/Rights & not covered & - & not covered & - \\
        21. Structures/Site & not covered & - & not covered & - \\
        22. Reactor Plant Equip. & not covered & - & not covered & - \\
        22.1 Reactor Equip. & not covered & - & not covered & - \\
        22.1.1 First Wall/Blanket & not covered & - & ECCN 1B233 & Lithium Isotopes \\
        22.1.2 High Temp. Shield & not covered & - & not covered & - \\
        22.1.3 Magnets & not covered & - & ECCN 1C005 & Superconducting composite \\
        22.1.4 Suppl. Heating & Sections III(8), II(5(d)) & Coaxial Plasma Gun & not covered & - \\
        22.1.5 Primary Structure & not covered & - & not covered & - \\
        22.1.6 Vacuum System & not covered & - & ECCN 1B230 & Low-temperature pumps \\
        22.1.7 Power Supplies & Section XI(5) & High Storage Capacitors & ECCN 3A001.e.2 & Capacitors \\
        22.1.11 Assembly and installation & not covered & - & not covered & - \\
        22.2 Main Heat Transfer & not covered & - & ECCN 1B233 & Lithium Isotopes \\
        22.3 Auxiliary Cooling & not covered & - & ECCN 1B999, 1B228 & Cooling $>$ 29.3 kW, Hydrogen cryo-distillation \\
        22.4 Rad. Waste Treat. & not covered & - & ECCN 1B999 & Cooling $>$ 29.3 kW \\
        22.5 Fuel Processing & not covered & - & ECCNs 1B233, 1E001, 1E201 & Tritium handling, development, use \\
        22.6 Other plant equipment & not covered & - & not covered & - \\
        22.7 Instrumentation and control & not covered & - & ECCN 3B992 & Particle measuring systems \\
        23. Turbine Plant Equip. & not covered & - & ECCN 1B232 & Turboexpanders \\
        24. Electric Plant Equip. & not covered & - & ECCN 3A980 & Electrical components \\
        25. Misc. Plant Equip. & not covered & - & not covered & - \\
        26. Heat Rejection & not covered & - & ECCN 1B999 & Cooling $>$ 29.3 kW \\
        27. Special Materials & not covered & - & not covered & - \\
        \hline  
    \end{tabular}}
    \caption{Cost accounts}
    \label{tab:costs}
\end{table}


\subsection{Regulations: EU}

The other key region considered in this report is the EU, which has analogous equipment categorizations to the United States' ITAR and EAR. In the EU, military arms are documented under the EU common military lists \cite{eu_common_military_list}, and dual use equipment under the EU Regulation 2021/821 \cite{europaEURLex32021R0821}. 


\begin{table}[h!]
    \centering
     \resizebox{1\linewidth}{!}{%
    \begin{tabular}{p{4cm}p{3cm}p{3cm}p{3cm}p{3cm}}
        \hline
        Cost Category & CML Coverage & Subsystem under CML & EU Dual-Use Coverage & Subsystem under EU Dual Use \\
        \hline  
        20. Land/Rights & not covered & - & not covered & - \\
        21. Structures/Site & not covered & - & not covered & - \\
        22. Reactor Plant Equip. & not covered & - & not covered & - \\
        22.1 Reactor Equip. & - & -& - & - \\
        22.1.1 First Wall/Blanket & - & - & 0B001-5 & Various \\
        22.1.2 High Temp. Shield & ML6, ML13 & HT and LT radiation shielding  & 2A290 & Specially designed materials \\
        22.1.3 Magnets & ML22 & Superconductive electrical equipment & 1E001,2 1B201, 1C002 & Superconducting composites \\
        22.1.4 Suppl. Heating & ML19 & Directed Energy Weapon & 3a001,2, 3d001, 3e001 & - \\
        22.1.5 Primary Structure & not covered & - & not covered & - \\
        22.1.6 Vacuum System & - & - & 2B233, 2B351, 2E003 & Vacuum or controlled atmosphere \\
        22.1.7 Power Supplies & M19 & High-Voltage Power Supplies & 3A225, 3A001, 3D001, 3E001 & Pulse generators \\
        22.1.8 Elctrodes or Plasma Guns & M19 & Directed Energy Weapon & not covered & - \\
        22.1.11 Assembly and installation & not covered & - & not covered & - \\
        22.2 Main Heat Transfer & - & - & 0B001-3, 0C002 & Handling fissile material \\
        22.3 Auxiliary Cooling & - & - & 2B350,1 2E002 & Materials processing \\
        22.4 Rad. Waste Treat. & - & - & 0B001-3, 0E001 & Handling fissile material \\
        22.5 Fuel Processing & - & - & 0B001 0B005, 0E001 & Reprocessing for irradiated fuel elements \\
        22.6 Other plant equipment & not covered & - & 0B005 & Reactor assembly and components \\
        22.7 Instrumentation and control & - & - & 3A001,2 3D001, 3E001 &  Electronic equipment and components \\
        23. Turbine Plant Equip. & - & - & 2B350, 3A001,2 3D001, 3E001 & Steam turbines \\
        24. Electric Plant Equip. & - & - & 3A001,2 3D001, 3E001 &  Electronic equipment and components \\
        25. Misc. Plant Equip. & not covered & - & 5A001,5D001 & Telecommunications security \\
        26. Heat Rejection & - & - & not covered & - \\
        27. Special Materials & not covered & - & not covered & - \\
        \hline  
    \end{tabular}}
    \caption{Cost accounts}
    \label{tab:costs}
\end{table}

\subsection{Existing Collaborations}