\subsubsection*{Cost Category 22.01.04: Ignition Lasers}

Inertial Fusion Energy (IFE) 'fast ignition' concepts employ highly specialized lasers, characterized by their high intensity and pulsed operation mode. These lasers emit energy in short, intense bursts, with peak power reaching petawatts, or a quadrillion watts. Additionally, the pulse duration of these lasers is remarkably brief, typically on the order of femtoseconds, which is one quadrillionth of a second. This ultra-short pulse duration is crucial for delivering the requisite energy to a small target area within an extremely brief timeframe, thereby creating the necessary conditions for initiating fusion.

   \begin{itemize} 
   \item Cost Category 22.01.04.01 Front End. This initial stage of the laser system is critical for generating the initial laser pulse. It sets the stage for subsequent amplification and conditioning, establishing the baseline characteristics of the laser pulse.
   \item Cost Category 22.01.04.02 Laser Amplification Subsystem. This subsystem involves multiple amplification stages that increase the energy of the laser pulse. Different types of amplifiers, such as solid-state or gas-based amplifiers, can be used.   
   \item Cost Category 22.01.04.03 Beam Transport Subsystem. This subsystem handles the precise transport of the laser beam from amplifiers to the target chamber. It includes optical components and beam-steering mechanisms.   
   \item Cost Category 22.01.04.04 Power conditioning system. Manages the electrical power needed for the laser system and ensures stable and reliable operation.
   \item Cost Category 22.01.04.05 Alignment and laser diagnostics.  Alignment and Calibration Subsystem: Maintains precise alignment of laser components to ensure accurate energy delivery to the target.
   \item Cost Category 22.01.04.06 Space frame. The space frame provides the structural support for the laser system. It ensures the physical stability and alignment of the various components, an aspect crucial for maintaining overall system integrity.
   \item Cost Category 22.01.04.07 Laser auxiliary systems. These systems encompass additional support mechanisms and technologies that assist in the operation and maintenance of the laser system, contributing to its overall functionality.
   \item Cost Category 22.01.04.08 Optics. The optics subsystem includes all the optical components involved in the laser system, such as lenses, mirrors, and diffraction gratings. They play a vital role in shaping, focusing, and directing the laser beam accurately towards its target.

   \end{itemize}   
   

\begin{table}[h!]
\centering
\resizebox{1\linewidth}{!}{%
\begin{tabular}{lcccc}
\hline
\textbf{Item} & \textbf{Procurement} & \textbf{Design} & \textbf{Assembly} & \textbf{Total} \\
\hline
22.1.3. Laser & 293.2 & 20.2 & 55.0 & 1115.3 \\
\hspace{5mm}22.1.3.1 Front End & 24.8 & 3.0 & 5.3 & 100.1 \\
\hspace{5mm}22.1.3.2 Main Amp System & 66.3 & 3.7 & 11.0 & 245.0 \\
\hspace{10mm}22.1.3.2.1 Main Amp & 28.2 & 1.7 & 3.4 & 100.5 \\
\hspace{15mm}22.1.3.2.1.1 Flashlamp Assemblies & 7.1 & 0.0 & 0.0 & 21.5 \\
\hspace{15mm}22.1.3.2.1.3, 3.2.1.5-7 (amp mech) & 21.1 & 1.7 & 3.4 & 79.1 \\
\hspace{10mm}22.1.3.2.2 Spatial filters & 9.1 & 0.2 & 2.0 & 34.0 \\
\hspace{10mm}22.1.3.2.3 Mirror Mounts & 3.3 & 0.0 & 0.3 & 11.1 \\
\hspace{10mm}22.1.3.2.4 Polarizer assembly & 1.7 & 0.2 & 0.9 & 8.6 \\
\hspace{10mm}22.1.3.2.5 Pockels' Cell Assembly & 17.4 & 1.6 & 3.7 & 68.4 \\
\hspace{10mm}22.1.3.2.6 Boost Amp & 5.9 & 0.0 & 0.7 & 20.1 \\
\hspace{15mm}22.1.3.2.6.1 Flashlamp Assemblies & 1.5 & 0.0 & 0.0 & 4.6 \\
\hspace{15mm}22.1.3.2.6.3, 3.2.6.5-7 (amp mech) & 4.4 & 0.0 & 0.7 & 15.5 \\
\hspace{10mm}22.1.3.2.7 Interstage Hdw & 0.8 & 0.0 & 0.0 & 2.5 \\
\hspace{5mm}22.1.3.3 Beam Xport system & 18.8 & 0.9 & 3.1 & 69.2 \\
\hspace{10mm}22.1.3.3.1 Spatial filters & 10.3 & 0.8 & 0.0 & 33.4 \\
\hspace{10mm}22.1.3.3.2 Mirror Assembly & 2.8 & 0.0 & 2.4 & 15.7 \\
\hspace{10mm}22.1.3.3.3 Final Optics system & 4.1 & 0.1 & 0.3 & 13.7 \\
\hspace{10mm}22.1.3.3.4 Beam Tube system & 1.6 & 0.0 & 0.4 & 6.3 \\
\hspace{10mm}22.1.3.3.5 Interstage Hdw & 0.0 & 0.0 & 0.0 & 0.1 \\
\hspace{5mm}22.1.3.4 Power cond system & 32.6 & 0.0 & 0.0 & 98.7 \\
\hspace{5mm}22.1.3.5 Align and Laser diag & 23.6 & 5.2 & 16.1 & 136.0 \\
\hspace{5mm}22.1.3.6 Space frame & 7.4 & 1.2 & 0.0 & 26.1 \\
\hspace{5mm}22.1.3.7 Laser aux systems & 0.5 & 0.0 & 1.3 & 5.5 \\
\hspace{5mm}22.1.3.8 Optics & 0.0 & 0.0 & 0.0 & 0.0 \\
\hline
\end{tabular}}
\caption{NIF Costs Breakdown}
\label{tab:nif_costs}
\end{table}



Cost category 22.01.04: ignition laser costs at  \$750/J for a 1.5MJ laser we get \$ C220103 M. 111502 M USD, totalling 1115 MUSD for the system.



